Trajectory Mapping Results

### 2021-03-25 scripts/analyze_trajectories.Rmd
initial commit

@@

```{r traj-data, warnings = FALSE, message = FALSE, cache = FALSE}
# Load trajectory data ---------------------------------------------------------
df <- loadTrajectories(args$args, burninFrac = args$burnin, subsample = args$n)

# Data wrangling ---------------------------------------------------------------
df_traj <- processEvents(df$events, demes, "China", MRS)
```

@@

## First imported cases to Europe, time and location
```{r first-eu-table}
knitr::kable(first_df1 %>%
               ungroup %>%
               count(deme, name = "n_1d") %>%
               mutate(p_1d = n_1d/args$n) %>%
               left_join(first_df10 %>%
                           ungroup %>%
                           count(deme,  name = "n_10d") %>%
                           mutate(p_10d = n_10d/(10*args$n)) %>%
                           left_join(first_df10 %>%
                                       ungroup %>%
                                       select(-deme) %>% rename(deme = partner) %>%
                                       count(deme,  name = "n_10s") %>%
                                       mutate(p_10s = n_10s/(10*args$n)))))
```

@@

:::: {.column width="50%"}
\small
```{r events-timing-table1}
knitr::kable((df_eventsttiming %>%
                group_by(deme, var) %>%
                summarise(m = median(date),
                          l = quantile(date, 0.025, type = 1),
                          h = quantile(date, 0.925, type = 1)))[1:12,])
```
::::

:::: {.column width="50%"}
\small
```{r events-timing-table2}
knitr::kable((df_eventsttiming %>%
                group_by(deme, var) %>%
                summarise(m = median(date),
                          l = quantile(date, 0.025, type = 1),
                          h = quantile(date, 0.925, type = 1)))[12:24,])
```

@@

```{r bvsm, fig.height=4}
h = df_traj %>%
  filter(var %in% c("B", "IM"), is.na(partner)) %>%
  select(-cumvalue) %>%
  group_by(deme, traj) %>%
  pivot_wider(names_from = "var", values_from = "value") %>%
  filter(IM != 0) %>%
  #na_if(0) %>% replace_na(list(B = 1e-8)) %>%
  mutate(R = B/IM) %>%
  mutate(R = ifelse(R == Inf, NA, R)) %>%
  select(traj, deme, date, R) %>%
  arrange(date) #%>%
#pivot_wider(names_from = date, values_from = R) %>%
#arrange(traj)

inpop = df_traj %>% filter(var == "in_pop", date == "2020-03-07") %>% select(traj, cumvalue)

hweek = df_traj %>%
  filter(var %in% c("B", "IM"), is.na(partner)) %>%
  select(-cumvalue) %>%
  group_by(deme, traj, var, year_week = ceiling_date(date, "1 week")) %>%
  summarize(value = sum(value)) %>%
  pivot_wider(names_from = "var", values_from = "value") %>%
  filter(IM != 0) %>%
  #na_if(0) %>% replace_na(list(B = 1e-8)) %>%
  mutate(R = B/IM) %>%
  mutate(R = ifelse(R == Inf, NA, R)) %>%
  select(traj, deme, year_week, R) %>%
  arrange(year_week)

hsummary = hweek %>% group_by(deme, year_week) %>% 
  summarise(mR = median(R),
            lR  = HDInterval::hdi(R)[[1]],
            hR  = HDInterval::hdi(R)[[2]])

@@

```{r bvsm-table, results = 'asis'}
for (d in demes$deme) {
  cat("\n## Local transmission vs imported cases - ", d, "\n")
  print(hsummary %>% filter(deme == d))
  cat("\n")
}
```

@@

\small
```{r incidence-table}
knitr::kable(df_inc %>% filter(date == max(date)))
```

>>>>

## Trajectory parameters

\tiny
```{r args-table}
knitr::kable(argsDF)
```

@@

```{r traj-data, warnings = FALSE, message = FALSE, cache = FALSE}
# Load trajectory data ---------------------------------------------------------
df <- loadTrajectories2(args$args, burninFrac = args$burnin, subsample = args$n)

# Data wrangling ---------------------------------------------------------------
df_traj <- processEvents(df, demes, "China", mrs)
```

@@

## First imported cases to Europe, time and location
```{r first-eu-table}
knitr::kable(first_df1 %>%
               ungroup %>%
               count(deme, name = "n_1d") %>%
               mutate(p_1d = n_1d/args$n) %>%
               full_join(first_df10 %>%
                           ungroup %>%
                           count(deme,  name = "n_10d") %>%
                           mutate(p_10d = n_10d/(10*args$n)) %>%
                           full_join(first_df10 %>%
                                       ungroup %>%
                                       select(-deme) %>% rename(deme = partner) %>%
                                       count(deme,  name = "n_10s") %>%
                                       mutate(p_10s = n_10s/(10*args$n)))))
```

@@

:::: {.column width="50%"}
\small
```{r events-timing-table1}
knitr::kable((df_eventsttiming %>% 
  left_join(first_ecdc %>% rename(ecdc_date = date)) %>%
  group_by(var, deme) %>%
  filter(date < ecdc_date) %>%
  count() %>%
  mutate(p = n/args$n))[1:12,])
```
::::

:::: {.column width="50%"}
\small
```{r events-timing-table2}
knitr::kable((df_eventsttiming %>% 
  left_join(first_ecdc %>% rename(ecdc_date = date)) %>%
  group_by(var, deme) %>%
  filter(date < ecdc_date) %>%
  count() %>%
  mutate(p = n/args$n))[12:24,])
```

@@

```{r bvsm, fig.height=4}
h <- df_traj %>%
  filter(var %in% c("B", "IM"), is.na(partner)) %>%
  select(-cumvalue) %>%
  group_by(deme, traj) %>%
  pivot_wider(names_from = "var", values_from = "value") %>%
  filter(IM != 0) %>%
  mutate(R = B/IM) %>%
  mutate(R = ifelse(R == Inf, NA, R)) %>%
  select(traj, deme, date, R) %>%
  arrange(date)

inpop <- df_traj %>% filter(var == "in_pop", date == "2020-03-07") %>% select(traj, cumvalue)

hweek <- df_traj %>%
  filter(var %in% c("B", "IM"), is.na(partner)) %>%
  select(-cumvalue) %>%
  group_by(deme, traj, var, year_week = ceiling_date(date, "1 week")) %>%
  summarize(value = sum(value)) %>%
  pivot_wider(names_from = "var", values_from = "value") %>%
  filter(IM != 0) %>%
  mutate(R = B/IM) %>%
  mutate(R = ifelse(R == Inf, NA, R)) %>%
  select(traj, deme, year_week, R, B, IM) %>%
  arrange(year_week)

hsummary = hweek %>% group_by(deme, year_week) %>% 
  summarise(mR = median(R),
            lR  = HDInterval::hdi(R)[[1]],
            hR  = HDInterval::hdi(R)[[2]],
            mB = median(B),
            mIM = median(IM))

@@

```{r bvsm-table, results = 'asis'}
for (d in demes$deme) {
  cat("\n## Local transmission vs imported cases - ", d, "\n")
  print(knitr::kable(hsummary %>% filter(deme == d)))
  cat("\n")
  cat("\n")}
```

@@

\small
```{r incidence-table}
knitr::kable(df_inc %>% filter(date == max(date)) %>% select(-date))
```
